Untitled

### 2024-08-27 code/manuscript_analysis.Rmd
make figures for manuscript

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))), 
          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

@@

#ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)

p.desc <- ggarrange(plot1, plot0, ncol = 2)

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
event_study(data = df.core, 
  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 1 ) 
p0

@@

#ggsave(filename = "Picture3a.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 9, height =16)

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
event_study(data = df.core, 
  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 3 ) 
p0

@@

# label1 <- 'beta[pooled] == "2.24**"'
# label2 <- 'beta[pooled] == "-0.21**"'
# 
# p0.simple <- ggarrange(
# event_study(data = df.core, 
#   yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
#   annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#         axis.title=element_text(size=14,face="bold")), 
# event_study(data = df.core, 
#   yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
#   annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#         axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
# p0.simple

#ggsave(filename = "Picture3ahSimple.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0.simple, width = 17, height = 9)

@@

#ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)

@@

  for (i in 1:5){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp.pats <- tes[-1,] %>% 
  cbind(Quantile = 1:5) %>% 
  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Estimate")

@@

#ggsave(filename = "Picture13pats.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp.pats, width = 16, height = 9)
```

@@

cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:2),]

df.spill3  %>% filter(Dist > quantile(Dist, 0.9) ) %>% 
  filter(Att > 0) %>% 
  group_by(Tx) %>% 
  summarise(mean(Total.Hours))

df.spill3 %>% filter(Dist < quantile(Dist, 0.2)) %>% 
  filter(Att > 0) %>%
  summarise(mean(Total.Hours))

@@

sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 62 & Year == Att - 1) %>% select(Total.Hours))

@@

>>>>

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))), 
          method = list("last.points", hjust = 1, vjust = c(2, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

@@

ggsave(filename = "Figure1.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.desc, width = 8, height = 11)

# p.desc <- ggarrange(plot1, plot0, ncol = 2) 
# 
# p.desc <- annotate_figure(p.desc, top = text_grob("FQHC Growth and Density by Zip and Clinic, UDS 1996 to 2021", face = "bold", size = 14))

@@

p0 <- ggarrange(
  event_study(data = df.core,
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 5) %>%
  filter(estimator == "Gardner (2021)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Quality Composite") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"),
event_study(data = df.core,
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 5) %>%
  filter(estimator == "Gardner (2021)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"),
event_study(data = df.core,
  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 5) %>%
  filter(estimator == "Gardner (2021)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Operational Efficiency") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff") , common.legend = TRUE, ncol = 1 )
p0

@@

ggsave(filename = "Figure2.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p0, width = 9, height =16)

label1 <- 'beta[pooled] == "2.24**"'
label2 <- 'beta[pooled] == "-0.21**"'
label3 <- 'beta[pooled] == "0.05**"'

# p0 <- ggarrange(
#   event_study(data = df.core, 
#   yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Quality Composite") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")+ 
#      annotate("text", x=2, y=-2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#      axis.title=element_text(size=14,face="bold")), 
# event_study(data = df.core, 
#   yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units")+ 
#      annotate("text", x=-2, y=-0.3, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#      axis.title=element_text(size=14,face="bold")), 
# event_study(data = df.core, 
#   yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Operational Efficiency") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff") + 
#      annotate("text", x=2, y=-0.05, label= label3, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#      axis.title=element_text(size=14,face="bold")) , common.legend = TRUE, ncol = 3 ) 
# p0

@@

@@

ggsave(filename = "Figure3.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p2, width = 17, height = 9)

@@

  for (i in 1:(length(qnats1))){
      model.dist.quants <-  did2s(
      data = df.spill3 %>%  filter((Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]) & Att > 0 ) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% mutate(Tx = ifelse(Att - 1 == Year & Att > 0 , 1, Tx))  %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp.pats <- tes[-1,] %>% 
  cbind(Quantile = 1:(length(qnats1))) %>% 
  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Estimate")

@@

#ggsave(filename = "Picture13pats.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp.pats, width = 16, height = 9)

summary(df.spill3$l.popdensity)
```

@@

cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:2),]
```

## Back of the envelop calculation, how much resources are reallocated?
```{r}

df.spill3  %>% filter(Dist > quantile(Dist, 0.8) ) %>% 
  filter(Att > 0) %>% 
  group_by(Tx) %>% 
  summarise(mean(Total.Hours))

df.spill3 %>% filter(Dist < quantile(Dist, 0.2)) %>% 
  filter(Att > 0) %>%
  group_by(Tx) %>% 
  summarise(mean(Total.Hours))

@@

sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > 0 & Year == Att - 1) %>% select(Total.Hours))

@@

#UPDATED AGAIN : 2.167812	* 	-0.427669x where X is in 10km increments

integrand <- function(x) {2.167812 + -0.0427669*x}
cutpoint <- 2.167812 / 0.0427669

areaUnder <- integrate(f = integrand, lower = cutpoint, upper = 200)
areaUnder$value / sum(df.spill3 %>% filter(Att > 0 & Dist < 200 & Dist > cutpoint & Year == Att - 1) %>% select(Total.Hours))

areaUnder <- integrate(f = integrand, lower = 0, upper = cutpoint)
areaUnder$value / sum(df.spill3 %>% filter(Att > 0 & Dist < cutpoint & Dist > 0 & Year == Att - 1) %>% select(Total.Hours))

did2s(
      data = df.spill3 %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

## Alternative Spec

Checking robustness of primary findings, allowing each FQHC to make shifting decisions within their own boarders... what happens? Simiarl story

```{r}
did2s(
      data = df.spill3 %>% 
        group_by(`BHCMIS ID`) %>% 
        arrange(`BHCMIS ID`, Dist) %>% 
        mutate(QuantClose = quantile(Dist, 0.333), 
               QuantFar = quantile(Dist, 0.666), 
               QuantMid = quantile(Dist, 0.5), 
               Denom = length(unique(Dist)), 
               Num = rank(Dist), 
               Quant = as.numeric((Dist - min(Dist)) / max(Dist)), 
               PopDensity = max(l.popdensity, na.rm = TRUE)) %>% filter(!is.na(Quant)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) %>% 
        mutate(MedicaidRate = Medicaid / NumberofPatients * 100, 
               UninsuredRate = Uninsured / NumberofPatients * 100), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ Sites| Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * as.numeric(Quant) * 10),
        cluster_var = "Zip",
      verbose = FALSE
    )
